The title

### 2022-09-27 paper/manuscript.Rmd
update participants
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

@@

<!-- ```{r methods, include = FALSE} -->
<!-- source(here("analysis/demographics", "questionnaire.R"), chdir = TRUE) -->
<!-- ``` -->

@@

20 participants were recruited who ---. Most participants were right-handed (left: ---). The mean age of the participants was --- (*SD* = ---). They had --- years of practice on average. All participants were recruited through an online participant platform (SONA system, https://www.sona-systems.com). The study (No. ---) was approved by the Psychological Research Ethics Board (PREBO) CEU PU in Austria.

@@

The experiment was programmed in Max/MSP (---; https://cycling74.com/products/max) on a Mac Book Pro with Mac OS X Catalina 10.15.6. A weighted Yamaha MIDI digital piano was used to record participants' performance. All auditory feedback was given to participants through headphones (Audio-Technica ATH-M50X). Sheet music was displayed on a computer monitor in front of the participants.

>>>>

```{r set-up, include = FALSE}
if (!require("papaja")) {install.packages("papaja"): require("papaja")}
if (!require("here")) {install.packages("here"): require("here")}
if (!require("magick")) {install.packages("magick"): require("magick")}
```

@@

```{r methods, include = FALSE}
source(here("analysis/demographics", "questionnaire.R"), chdir = TRUE)
source(here("analysis/demographics", "questionnaire.R"), chdir = TRUE)
```

@@

`r nrow(dt_included)` participants were recruited who already had a degree (above bachelor or equivalent) in piano performance/teaching or were studying advanced piano performance at a music school. Most participants were right-handed (left: `r nrow(dt_included[Handedness == "Left"])`, ambidextrous: `r nrow(dt_included[Handedness == "Both"])`). The mean age of the participants was `r round(mean(dt_included$Age), 2)` (*SD* = `r round(sd(dt_included$Age), 2)`). They had `r round(mean(dt_included$PianoTotalPractice), 2)` years of practice on average (*SD* = `r round(sd(dt_included$PianoTotalPractice), 2)`). `r nrow(dt_included[TeachingPiano == "Yes"])` participants had teaching experience in piano (*M* = `r round( mean(dt_included[TeachingPiano == "Yes"]$TeachingPianoYears), 2)` years, *SD* = `r round(sd(dt_included[TeachingPiano == "Yes"]$TeachingPianoYears), 2)`). All participants were recruited through an online participant platform (SONA system, https://www.sona-systems.com). The study (No. 2020_05) was approved by the Psychological Research Ethics Board (PREBO) CEU PU in Austria.

@@

The experiment was programmed in Max/MSP (8.1.11; https://cycling74.com/products/max) on a Mac Book Pro with Mac OS X Catalina 10.15.7. A weighted Yamaha MIDI digital piano was used to record participants' performance. All auditory feedback was given to participants through headphones (Audio-Technica ATH-M50X). Sheet music was displayed on a computer monitor in front of the participants.

### 2022-09-27 paper/manuscript.tex
update participants
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

20 participants were recruited who ---. Most participants were right-handed (left: ---). The mean age of the participants was --- (\emph{SD} = ---). They had --- years of practice on average. All participants were recruited through an online participant platform (SONA system, \url{https://www.sona-systems.com}). The study (No.~---) was approved by the Psychological Research Ethics Board (PREBO) CEU PU in Austria.

@@

The experiment was programmed in Max/MSP (---; \url{https://cycling74.com/products/max}) on a Mac Book Pro with Mac OS X Catalina 10.15.6. A weighted Yamaha MIDI digital piano was used to record participants' performance. All auditory feedback was given to participants through headphones (Audio-Technica ATH-M50X). Sheet music was displayed on a computer monitor in front of the participants.

>>>>

20 participants were recruited who already had a degree (above bachelor or equivalent) in piano performance/teaching or were studying advanced piano performance at a music school. Most participants were right-handed (left: 2, ambidextrous: 2). The mean age of the participants was 28.25 (\emph{SD} = 10.95). They had 21.55 years of practice on average (\emph{SD} = 11.59). 17 participants had teaching experience in piano (\emph{M} = 7 years, \emph{SD} = 6.68). All participants were recruited through an online participant platform (SONA system, \url{https://www.sona-systems.com}). The study (No.~2020\_05) was approved by the Psychological Research Ethics Board (PREBO) CEU PU in Austria.

@@

The experiment was programmed in Max/MSP (8.1.11; \url{https://cycling74.com/products/max}) on a Mac Book Pro with Mac OS X Catalina 10.15.7. A weighted Yamaha MIDI digital piano was used to record participants' performance. All auditory feedback was given to participants through headphones (Audio-Technica ATH-M50X). Sheet music was displayed on a computer monitor in front of the participants.
